---
title: Ocean Accounts
subtitle: Day 1 Thinking
author: James Hogan, Senior Marine Resource Economist, FAME - SPC
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
   bookdown::word_document2:
      reference_docx: "S:\\FAME\\NC_NOU\\FAME COMMON\\FAME Economics\\Oceans_Accounts\\Product_Output\\Blank_Word_Template.docx"
      toc: false  
      fig_caption: true
      number_sections: true
      global_numbering: true  
      
header-includes:
   - \usepackage[percent]{overpic}   
   - \usepackage{tikz}
   - \usetikzlibrary{calc}
   - \usepackage{graphicx}
   - \usepackage{placeins}
   - \usepackage{fancyhdr}
   - \pagestyle{fancy}
   - \fancyhf{}
   - \addtolength{\headwidth}{\marginparsep}
   - \addtolength{\headwidth}{\marginparwidth}   
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}

   
---
\newpage


```{r setup, cache=FALSE, include=FALSE}

##
##    Core libraries
##
      library(ggplot2)
      library(plyr)
      library(stringr)
      library(lubridate)
      library(calibrate)
      library(Hmisc)
      library(RColorBrewer)
      library(stringi)
      library(sqldf)
      library(scales)
      library(RDCOMClient)
      library(extrafont)
      library(tictoc)
      library(RODBC)
      
      library(sysfonts)
      library(showtext)
##
##    Project-specific libraries
##
      library(knitr)
      library(citr)
      library(htmlTable)
      library(bookdown)
      library(kableExtra)
      library(pander)
      library(officer)


      library(RefManageR)

      BaseDir <- "S:\\FAME\\NC_NOU\\FAME COMMON\\FAME Economics\\Oceans_Accounts\\Graphical_Output\\"
  
  
##
##    Grab my Bibliography - where do you find the collection key from? https://forums.zotero.org/discussion/18400/collectionid-collectionkey
##       Its found on the web version of your library - of course... ;)
##
##       The key is an API access key created in Zotero online under JamesHogan1\Settings\Security\Applications area => "create new private key"
##       The Collection ID is found from the URL when you click into the collection: https://www.zotero.org/jameshogan1/collections/QCYI7BUU
##
      Biib <- ReadZotero(user = '14637827', .params = list(key = '0RTmBtbkHWkStie80fRsfVdn', collection = 'QCYI7BUU')) # Reads in James Hogan's "Ocean Accounting" bibliography
      BibOptions(check.entries = FALSE, style = "markdown", cite.style = "authoryear", bib.style = "numeric",first.inits = TRUE)

```

   

<!-- 
##
##       This bit below is the commentary written in R Markup
-->
 
*	What are they?

      * SEEA-based versus GOAP(?)
      * Sea-based capital versus land-based capital[^Page23]
      * Economics flows come from productive capital
      * Sea-based capital is:
         * Economically productive
         * Affected by climate change differently
         * Creates a separate source of economic flows, compared to land-based capital


*	Who will use them?

      *	Member countries
      *	Donors/funders
   
*	What problem(s) will they solve?

      *	Made at scale and all at once, they enable countries to be compared
      *	Bring together fisheries assets & fisheries revenues

*	Data

      *	Digital Earth Pacific data sources
      *	FAME Fisheries Stocks
      *	GEM Minerals

*	Advisory group

      *	Lisa Green
      *	Tony
      *	Jens
      *	Tiffany

*	Governance Group

      *	Process with the members
      *	Finances – who is this being paid for?
      *	Engagement – what’s the relationship between GOAP and SPC? Where does SPREP feature in this picture?
      *	Members
         *	Peter Ellis 
         *	Neville Smith
         *	Karen Mu
         
*	What do these things look like?
      *	Based off the SEEA – look for real examples
      *	Geospatial version
      *	Statistical reporting version (a set of accounts)
   
*	Important people
      *	Anne-Claire Goarant
      *	Espen Ronneberg
      *	Lisa Green
      *	Lucie Kuczynski
   
*	Connection with
      *	Palau Marine Spatial Planning
      *	Biodiversity metrics – SPREP Indicators
      *	Economic connections 
         *	Tuna revenues
         *	Petroleum Revenues?



# References

```{r results = "asis", echo = FALSE}
PrintBibliography(Biib, .opts = list(check.entries = FALSE, sorting = "ynt"))
```